---
title: "Music Genre Sentiment Analysis--R Code"
author: "Julie Bazalewski"
date: "06/20/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Overview

Analyze data from #countrymusic, #rockmusic, and #popmusic Twitter tags to determine if genre affects tweet sentiment.

```{r include=FALSE}
library(readr)
library(dplyr)
library(ggformula)
```
## Import .csv file

```{r}
tweet_df = read_csv("tweets_3147.csv", n_max = 3147)
summary(tweet_df)
```
## Group by Genre and create boxplot

```{r}
gf_boxplot(sentiment ~ genre, data = tweet_df, fill=~genre)%>% 
  gf_refine(scale_fill_manual(values = c("tomato2","cyan3", "sienna4")))
```

```{r}
#look at histograms
gf_histogram(~sentiment, data=tweet_df, fill="turquoise", color="black") %>% gf_facet_grid(genre~.)
```
## Calculate mean sentiment of each genre
```{r}
genreSentiment <- tweet_df %>% 
  group_by(genre) %>%
  summarise(genre.mean = mean(sentiment)) %>%
  arrange(desc(genre.mean))

genreSentiment
```
## Perform Chi Squared Test of Independence using sentiment as a categorial variable (negative, neutral, or positive)
H0: There is no relationship between music genre and sentiment type
H1: There is a relationship between music genre and sentiment type

```{r}
#turn sentiment into a categorical variable
tweet_df <- tweet_df %>% 
  mutate(sentiment_type = case_when(sentiment<0 ~"Negative", sentiment > 0 ~"Positive", TRUE ~"Netural"))

#perform chi squared test
chisq.test(tweet_df$genre, tweet_df$sentiment_type)
```
## Conclusion: 
At the alpha = 0.05 significance level there is enough evidence to claim that there is an association between genre and sentiment.


## Perform Kruskal-Wallis test as an alternative to ANOVA to check sentiment between groups with sentiment as a non-normal, numerical variable 
H0: There is no relationship between music genre and sentiment
H1: There is a relationship between music genre and sentiment

```{r}
kruskal.test(sentiment ~ genre, data = tweet_df)
```
## Conclusion: 
At the alpha = 0.01 significance level there is enough evidence to claim that there is an association between genre and sentiment.

## Perform T-Tests, the data is not normally distributed but the sample sizes are large. Use numerical sentiment data rather than categorical.
```{r}
country_sentiment = tweet_df$sentiment[which(tweet_df$genre == 'country')]
rock_sentiment = tweet_df$sentiment[which(tweet_df$genre == 'rock')]
pop_sentiment = tweet_df$sentiment[which(tweet_df$genre == 'pop')]

t.test(country_sentiment,rock_sentiment, alternative="less")
t.test(country_sentiment,rock_sentiment, alternative="greater")

t.test(country_sentiment,pop_sentiment, alternative="less")
t.test(country_sentiment,pop_sentiment, alternative="greater")

t.test(rock_sentiment,pop_sentiment, alternative="less")
t.test(rock_sentiment,pop_sentiment, alternative="greater")
```
##Conclusions:
I looked at one-tail t-tests between each genre in both directions. I found that there is evidence at a significance level of alpha = 0.01 that the true sentiment of the pop tweets is greater than the sentiment of the rock tweets. I also found that there is evidence at a signficiance level of alpha = 0.05 that the true sentiment of the country tweets is greater than the sentiment of the rock tweets. I did not find evidence that the mean of the pop and country tweets differ significantly.

#Summarize location data. Used to filter tweets in python code by finding large numbers of tweets from unexpected locations.
```{r}
country_locationCount <- tweet_df %>% 
  filter(genre == "country") %>%
  group_by(location) %>%
  summarise(location.count = n()) %>%
  arrange(desc(location.count))

rock_locationCount <- tweet_df %>% 
  filter(genre == "rock") %>%
  group_by(location) %>%
  summarise(location.count = n()) %>%
  arrange(desc(location.count))

pop_locationCount <- tweet_df %>% 
  filter(genre == "pop") %>%
  group_by(location) %>%
  summarise(location.count = n()) %>%
  arrange(desc(location.count))

```